### 2015-03-05 ThesisJo/derivations.tex
la2pdf commit - 2015:03:05	14:50:56	(Thu 5.Mar)

\begin{align}
\nabla\cdot(-\nabla s') &= \nabla\cdot\Big(\rho_0 \frac{\partial\v'}{\partial t}\Big) &
\frac{\partial}{\partial t}\frac{\partial\rho'}{\partial t} &= \frac{\partial}{\partial t}\Big(-\rho_0\nabla \cdot \v'\Big)\nn
-\nabla^2 s' &= \rho_0 \nabla\cdot\frac{\partial\v'}{\partial t} &
\frac{\partial^2\rho'}{\partial t^2} &= \frac{1}{c^2}\frac{\partial^2 s}{\partial t^2} = -\rho_0\nabla\cdot\frac{\partial \v'}{\partial t}
\end{align}
%
and we can now see that
%
\begin{align}
\nabla^2 s' - \frac{1}{c^2}\frac{\partial^2 s'}{\partial t^2} = 0.
\end{align}
%
This is called the homogeneous lossless wave equation, because there is no source term. When our signal $s$ signifies pressure (N/m$^2$), this links time and space by means of mass flow rate (kg/(m$^3$s). The inhomogeneous equation can be obtained in a similar way, by altering the linearized continuity equation to include a source:
%
\begin{align}
\frac{\partial\rho'}{\partial t} &= -\rho_0\nabla \cdot \v' - \rho_0f(\p,t). \label{wave_eq_mass_conservation_source}
\end{align}
%
where $\rho_0f(\p,t)$ is the rate of mass change (in $\left[\frac{\text{kg}}{\text{m}^3\text{s}}\right]$) caused by the source. Following the exact same procedure as before we obtain:
%
\begin{align}
\nabla^2 s' - \frac{1}{c^2}\frac{\partial^2 s'}{\partial t^2} = \rho_0\frac{\partial f(\p,t)}{\partial t}.
\end{align}
%

@@

Now let us choose a trigonometric window function:
%
\begin{align}
\w = \frac{e^{j\varphi}}{2\pi\alpha}\big(\alpha + (1-\alpha)\cos\left(\frac{2\pi n}{N-1}\right)\big)
\end{align}
%
Inserting this yields:
%
\begin{align}
\w\H\x &= \sumb{m=0}{M-1} e^{j\varphi}\Big(\alpha + (1-\alpha)\cos\theta\Big) x_m^* \nn
&= \sumb{m=0}{M-1} e^{j\varphi}\Big(\alpha + (1-\alpha)\cos\theta\Big) x_m^*
\end{align}
%
where $\theta = \frac{2\pi n}{N-1}$.

>>>>

\begin{align}
\nabla\cdot(-\nabla s') &= \nabla\cdot\Big(\rho_0 \frac{\partial\v'}{\partial t}\Big) &
\frac{\partial}{\partial t}\frac{\partial\rho'}{\partial t} &= \frac{\partial}{\partial t}\Big(-\rho_0\nabla \cdot \v'\Big)\nn
-\nabla^2 s' &= \rho_0 \nabla\cdot\frac{\partial\v'}{\partial t} &
\frac{\partial^2\rho'}{\partial t^2} &= \frac{1}{c^2}\frac{\partial^2 s}{\partial t^2} = -\rho_0\nabla\cdot\frac{\partial \v'}{\partial t}
\end{align}
%
and we can now see that
%
\begin{align}
\nabla^2 s' - \frac{1}{c^2}\frac{\partial^2 s'}{\partial t^2} = 0.
\end{align}
%
This is called the homogeneous lossless wave equation, because there is no source term. When our signal $s$ signifies pressure (N/m$^2$), this links time and space by means of mass flow rate (kg/(m$^3$s).

The inhomogeneous equation can be obtained in a similar way by including a source term. If we model the source as an injection of a volume of fluid, we can include it in the linearized continuity equation:
%
\begin{align}
\frac{\partial\rho'}{\partial t} &= -\rho_0\nabla \cdot \v' - \rho_0f(\p,t). \label{wave_eq_mass_conservation_source}
\end{align}
%
where $\rho_0f(\p,t)$ is the rate of mass change (in $\left[\frac{\text{kg}}{\text{m}^3\text{s}}\right]$) caused by the mass injection. Following the exact same procedure as before we obtain:
%
\begin{align}
\nabla^2 s' - \frac{1}{c^2}\frac{\partial^2 s'}{\partial t^2} = \rho_0\frac{\partial f(\p,t)}{\partial t}.
\end{align}
%

@@

Now let us choose a trigonometric window function:
%
\begin{align}
\w = \frac{e^{j\varphi}}{2\pi\alpha}\big(\alpha + (1-\alpha)\cos\left(\frac{2\pi m}{M-1}\right)\big)
\end{align}
%
Inserting this yields:
%
\begin{align}
\w\H\x &= \sumb{m=0}{M-1} e^{j\varphi}\Big(\alpha + (1-\alpha)\cos\theta[n]\Big) x_m^* \nn
&= \sumb{m=0}{M-1} e^{j\varphi}\Big(\alpha + (1-\alpha)\cos\theta[n]\Big) x_m^*
\end{align}
%
where $\theta = \frac{2\pi n}{N-1}$.
